### 2021-10-27 README.Rmd
Add DOCKERFILE
Incorporate co-author feedback

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///main?urlpath=rstudio)

@@

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/FlukeAndFeather/cetaceanbcg/main?urlpath=rstudio)

@@

You can download the compendium as a zip from from this URL:
[main.zip](/archive/main.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console
